---
title: "Superstore Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(plotly)
library(tidyverse)
ssdata <- read.csv("C:\\Users\\user\\Downloads\\SampleSuperstore.csv")
ssdatanew <- ssdata %>% distinct()
maxSales <- max(ssdatanew$Sales)
ssdatanew$Sales <- replace(ssdatanew$Sales, ssdatanew$Sales==maxSales, mean(ssdatanew$Sales))
ssdatanew <- ssdatanew %>% select(-c(Country, Postal.Code))
```

Row {data-width=350}
-----------------------------------------------------------------------
### Sales and Quantity for different shipment modes

```{r}
p <- ggplot(data = ssdatanew, aes(x = Quantity, y = Sales, fill = Ship.Mode) )+ geom_bar(stat = "identity") 
ggplotly(p)

```

>Most of the sales have been triggered by the standard class of shipment mode.

### Profit and Sales for different shipment modes

```{r}
p1 <- ggplot(data = ssdatanew, aes(x = Sales, y = Profit, color = Ship.Mode)) + geom_point()
ggplotly(p1)


```

>More profits have been availed from the standard shipment class, but the range of profits remain low.

Row {data-width=350}
-----------------------------------------------------------------------

### Sales and Discount for different shipment modes

```{r}
p2 <- ggplot() + geom_point(data = ssdatanew, aes(x = Discount, y = Sales, color = Ship.Mode)) 
ggplotly(p2)

```


### Profits and Discount for different shipment modes

```{r}
p3 <- ggplot() + geom_bar(data = ssdatanew, aes(x = Discount, y = Profit, fill = Ship.Mode), stat = "identity") 
ggplotly(p3)

```

>Products with no discounts show high range of profits, but as the discount range increases, more loss and less profit can be seen.


Row {data-width=650}
-----------------------------------------------------------------------
### Profits for different Subcategories

```{r}
p4 <-ggplot() + geom_bar(data = ssdatanew, aes(x = Sub.Category, y = Profit, fill = Region), stat = "identity") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
ggplotly(p4)

```

>Most losses have been incurred by the Binders sub category mainly in the Central region. Machines and Tables sub categories also show substantial losses.

Row {data-width=225}
-----------------------------------------------------------------------
### Profits And Sales sorted by Categories  

```{r}
p7 <- ggplot() + geom_point(data = ssdatanew, aes(x = Sales, y = Profit, color = Category)) 
ggplotly(p7)
```

>For all categories the points cluster around the same area. So sales to profit ratio is almost same across categories except for few data points.


### Sales sorted by Categories and Regions 

```{r}
p5 <- ggplot() + geom_bar(data = ssdatanew, aes(x = Category, y = Sales, fill = Region), stat = "identity") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
ggplotly(p5)

```

>Most Sales have been made by the Technology Industry, followed by Furniture and Office supplies industry. Majorly sales have been made in the West and East regions.

### Profits sorted by Categories and Regions 

```{r}
p6 <- ggplot() + geom_bar(data = ssdatanew, aes(x = Category, y = Profit, fill = Region), stat = "identity") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
ggplotly(p6)

```

>The Furniture Industry incurred most losses followed by Office Supplies and Technology Industry.

Row {data-width=350}
-----------------------------------------------------------------------

### Analysis

1. If Same day shipment mode receives more discounts it can trigger sales and profits. 

2. Discounts should be based on sales, otherwise unnecessary discounts with low sales can witness huge losses.

3. Binders, Machines and Tables sub category are lagging behind and should be focused upon more to strengthen them.

4. Office Supplies and the Furniture industries do not seem to boom in the Central Region (as can be seen by quite large losses).


